---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

# Loading required libraries
library(tidyverse)

# --- Data Loading and Cleaning ---
logged_data <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vSCxmMtd1FbYWvFXUACUMXUx9DES1edYFnjzlgpFBFFmHOXDqwhF0ewpp1ikgFio5cG52ZuPASb1Vjf/pub?gid=1192164059&single=true&output=csv")

latest_data <- logged_data %>% 
  rename(time_int = 2, n_cars = 3, logged_day = 4)

# Defining order of days for factors and time intervals
day_levels <- c("Saturday", "Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
time_levels <- c("2 am - 6 am", "6 am - 10 am", "10 am - 2 pm", "2 pm - 6 pm", "6 pm - 10 pm", "10 pm - 2 am")

latest_data <- latest_data %>%
  mutate(logged_day = factor(logged_day, levels = day_levels)) %>%
  mutate(time_int = factor(time_int, levels = time_levels))

# --- Summary Values for Dynamic Comments ---
overall_avg <- mean(latest_data$n_cars, na.rm = TRUE)
peak_occupancy <- max(latest_data$n_cars, na.rm = TRUE)
total_logs <- nrow(latest_data)
```

```{css}

body {
  font-family: 'Helvetica', sans-serif;
  color: #2c3e50;
  line-height: 1.6;
}

h2 {
  color: #2980b9;
  border-bottom: 2px solid #eee;
  padding-bottom: 10px;
}

.report-summary {
  background-color: #f9f9f9;
  padding: 15px;
  border-radius: 8px;
  border-left: 5px solid #2980b9;
}

```

## Analysis of Car Park Occupancy at Carlaw Park Student Village   

This report analyzes car parking patterns based on `r total_logs` recorded observations. By tracking the number of cars parked across different days and time intervals, we can identify peak usage periods.

r paste0("The data shows that the average number of cars parked across all sessions is ", round(overall_avg), ".")

additionally, the highest level of occupancy recorded in this period reached a peak of r peak_occupancy cars.

Weekly Usage Trends
The following chart illustrates how parking demand fluctuates throughout the week.

```{r}
# Chart 1: Average Parked Cars per Day
latest_data %>%
  group_by(logged_day) %>% 
  summarise(avg_cars = mean(n_cars, na.rm = TRUE)) %>% 
  ggplot(aes(x = logged_day, y = avg_cars)) + 
  geom_col(fill = "steelblue") +
  labs(
    title = "Average Parked Cars per Day",
    x = "Day of the Week",
    y = "Average Number of Cars"
  ) +
  theme_minimal()
```

Time Interval Distribution
This visualization identifies which times of the day experience the highest volume of parked vehicles.

```{r}
# Chart 2: Average parked cars per Time Interval 
latest_data %>%
  group_by(time_int) %>%
  summarise(avg_cars = mean(n_cars, na.rm = TRUE)) %>% 
  ggplot(aes(x = time_int, y = avg_cars)) + 
  geom_col(fill = "cyan", width = 0.7) + 
  labs(
    title = "Average Parked Cars by Time Intervals",
    x = "Time Intervals", 
    y = "Average Number of Cars"
  ) + 
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```
